SPARQL on the open, decentralised Web

### 2016-06-05 dissertation/introdefhistory.tex
proofread

In 1996, I started the Web pages of the Norwegian Skeptics Society
\texttt{skepsis.no}, and therefore got the control over an entire Web
server. That was another revelation, as I could actually run code, and
from that arose the need to not just learn by ``View Source'', but
start to read the specifications, notably HTML, CSS and
HTTP. Appreciating the design of these specifications took a while,
but eventually, the value of orthogonal specifications and separation
of concerns became apparent. Also, at the same time, I realised that I
could be standing on the shoulders of giants by using Free Software.

@@

However, all the above had happened on my spare time, as the topic of
my study was something else entirely: Cosmology, and so the interest
lay dormant for a few years as I finished my Cand. Scient.-degree. 
After that, I got some limited funding to write what today would be
called a Semantic Content Management System. The project was far too
ambitious and largely a failure, but it got me some valuable
experience with Semantic Web technology.

@@

However, it became clear that I could not have sufficient time in the
industry to pursue what was developing as my main interest, query
answering over data on the open Web, for generic application
development.

>>>>

In 1996, I started the Web pages of the \textit{Norwegian Skeptics Society}
\texttt{skepsis.no}, and therefore got the control over an entire Web
server. That was another revelation, as I could actually run code, and
from that arose the need to not just learn by ``View Source'', but
start to read the specifications, notably HTML, CSS and
HTTP. Appreciating the design of these specifications took a while,
but eventually, the value of orthogonal specifications and separation
of concerns became apparent. Also, at the same time, I realised that I
could be standing on the shoulders of giants by using Free Software.

@@

However, all the above had happened on my spare time, as the topic of
my study was something else entirely: Cosmology. Therefore, the
interest lay dormant for a few years as I finished my
Cand. Scient.-degree.  After that, I got some limited funding to write
what today would be called a Semantic Content Management System. The
project was far too ambitious and largely a failure, but it got me
some valuable experience with Semantic Web technology.

@@

However, it became clear that I could not have sufficient time in the
industry to pursue what was developing as my main interest, query
answering over data on the open Web for generic application
development.
